\documentclass[a4paper]{willianpaixao-resume}

\begin{document}
\name{\bfseries Willian Paixao}
%\begin{letter}{\bfseries Visual Meta GmbH\\Schützenstraße 25\\10117 Berlin\\Germany}
\begin{letter}{\bfseries
Delivery Hero Holding GmbH\\Mohrenstraße 60\\10117 Berlin\\Germany}
\opening{Good morning,}
%\cc{Mr Schultheiß}

I'm a Brazilian Computer Engineering, graduating in September who has worked
both as Developer and Linux System Administrator since 2009. I love code and I
double love coding in GNU/Linux.

Recently the new role called DevOps has been my dream career because it joins
everything I do with passion. I'm very proactive, professional and work for the
team. Your job offer gathers many technologies I like and all the benefits from
working in a startup in the heart of Berlin really attracts me.

%My passion for computers started as early as my childhood memories. I never had
%never doubts I would choose a different career. At the age of fourteen I started
%programming in web languages, at the same time I installed my first GNU/Linux
%distribution.

%With seventeen years I got accepted at the best university of Amazon region and
%after the first semester I started to work for Ericsson in a research laboratory
%as a Java Developer. Two years later I had the great opportunity to work with
%Java again when I was hired by Siemens for a year as Software Engineer intern in
%the United States.

%So I have ten years of programming experience, seven of them as a professional.
%However my passion has always been Linux and servers. In 2012 I was hired by the
%biggest Linux support company of Amazon region. The company provides high level
%support to servers and services to lots of malls, big supermarket chains and
%telecom companies, numerous malls and big supermarket chains As there was so
%much work and things to learn I suspended my college degree for one semester. In
%this way I could dive into the technology stack and acquired as much knowledge
%as my time allowed me. After getting my LIPC certification I was promoted to
%LPIC instructor as a second role. So I taught Linux as part time. I even helped
%to improve the company's guide book for the students. Since certification has an
%expiration date of three years and since I didn't renew it yet, I am not allowed
%to add it to my resumé.

%When I returned from the USA, I accepted an offer to work in my University's
%datacenter, which is still my current job and passion. Meanwhile I was able to
%make many changes there, including bringing new technologies and methodologies.
%The campus has about sixty thousand students and therefore it is not easy to
%keep our infrastructure running smoothly. I will graduate in September and my
%contract doesn't allow me to work without being a student. In another words, I
%will be free and motivated to fulfill my job as an engineer in a new company.

I have a big dream of living in Germany since many years. I attended a German
course for three years and got a Goethe-Zertifikat B1, which I cannot attach to
my resumé, for the same reason of the LPIC, it is expired. Since it is really
hard to speak German here in my hometown, my fluency level also decreased due to
lack of training, but this year while spending my vacations in Germany I had no
problems to express myself.

In the job offer you mention starting date and salary expectations. For the
first issue, mid September seems a great time, due to my graduation and the end
of my current working contract. Regarding the salary, I have to admit that it is
a tricky question. Berlin is an expensive city and I am looking for a position
higher than Junior. However I have never worked for the money, so do you think
47k € before taxes is fair enough?

I look forward to hearing from you. Have an awesome week.
\closing{Kind regards,}
\end{letter}
\end{document}
